P versus NP

### 2019-12-31 doc/manuscript.tex
Finalized the doc proof

%TODO mandatory: add short abstract of the document
\begin{abstract}
P versus NP is considered as one of the most important open problems in computer science. This consists in knowing the answer of the following question: Is P equal to NP? A precise statement of the P versus NP problem was introduced independently by Stephen Cook and Leonid Levin. Since that date, all efforts to find a proof for this problem have failed. Another major complexity classes are L and NL. We demonstrate if L is not equal to NL, then P = NP. In addition, we show if L is equal to NL, then P = NP. In this way, we prove the complexity class P is equal to NP. Furthermore, we demonstrate the complexity class NL is equal to NP.
\end{abstract}

@@

The $P$ versus $NP$ problem is a major unsolved problem in computer science \cite{CS00}. This is considered by many to be the most important open problem in the field \cite{CS00}. It is one of the seven Millennium Prize Problems selected by the Clay Mathematics Institute to carry a US\$1,000,000 prize for the first correct solution \cite{CS00}. It was essentially mentioned in 1955 from a letter written by John Nash to the United States National Security Agency \cite{AS17}. However, the precise statement of the $P=NP$ problem was introduced in 1971 by Stephen Cook in a seminal paper \cite{CS00}. In 2012, a poll of 151 researchers showed that 126 (83\%) believed the answer to be no, 12 (9\%) believed the answer is yes, 5 (3\%) believed the question may be independent of the currently accepted axioms and therefore impossible to prove or disprove, 8 (5\%) said either do not know or do not care or don't want the answer to be yes nor the problem to be resolved \cite{GA12}. It is fully expected that $P \neq NP$ \cite{Pap03}. Indeed, if $P = NP$ then there are stunning practical consequences \cite{Pap03}. For that reason, $P = NP$ is considered as a very unlikely event \cite{Pap03}. Certainly, $P$ versus $NP$ is one of the greatest open problems in science and a correct solution for this incognita will have a great impact not only in computer science, but for many other fields as well \cite{AS17}. Whether $P = NP$ or not is still a controversial and unsolved problem \cite{AS17}. We show some results that prove this outstanding problem with the unexpected solution of $P = NP$.

@@

\begin{enumerate}
\item Cryptography, for example, relies on certain problems being difficult. A constructive and efficient solution to an $\textit{NP--complete}$ problem such as $3SAT$ will break most existing cryptosystems including: Public-key cryptography \cite{HW97}, symmetric ciphers \cite{MM00} and one-way functions used in cryptographic hashing \cite{DKV07}. These would need to be modified or replaced by information-theoretically secure solutions not inherently based on $\textit{P--NP}$ equivalence.
\item There are enormous positive consequences that will follow from rendering tractable many currently mathematically intractable problems. For instance, many problems in operations research are $\textit{NP--complete}$, such as some types of integer programming and the traveling salesman problem \cite{GJ79}. Efficient solutions to these problems have enormous implications for logistics \cite{CS00}. Many other important problems, such as some problems in protein structure prediction, are also $\textit{NP--complete}$, so this will spur considerable advances in biology \cite{BL98}.
\item Since all the $\textit{NP--complete}$ optimization problems become easy, everything will be much more efficient \cite{LF09}. Transportation of all forms will be scheduled optimally to move people and goods around quicker and cheaper \cite{LF09}. Manufacturers can improve their production to increase speed and create less waste \cite{LF09}. Learning becomes easy by using the principle of Occam's razor: We simply find the smallest program consistent with the data \cite{LF09}. Near perfect vision recognition, language comprehension and translation and all other learning tasks become trivial \cite{LF09}. We will also have much better predictions of weather and earthquakes and other natural phenomenon \cite{LF09}.
\item There would be disruption, including maybe displacing programmers \cite{IMP95}. The practice of programming itself would be more about gathering training data and less about writing code \cite{IMP95}. Google would have the resources to excel in such a world \cite{IMP95}.
\item But such changes may pale in significance compared to the revolution an efficient method for solving $\textit{NP--complete}$ problems will cause in mathematics itself \cite{CS00}. Research mathematicians spend their careers trying to prove theorems, and some proofs have taken decades or even centuries to find after problems have been stated \cite{AS17}. For instance, Fermat's Last Theorem took over three centuries to prove \cite{AS17}. A method that is guaranteed to find proofs to theorems, should one exist of a $``$reasonable$"$ size, would essentially end this struggle \cite{CS00}.
\end{enumerate}

>>>>

%TODO mandatory: add short abstract of the document
\begin{abstract}
P versus NP is considered as one of the most important open problems in computer science. This consists in knowing the answer of the following question: Is P equal to NP? It was essentially mentioned in 1955 from a letter written by John Nash to the United States National Security Agency. However, a precise statement of the P versus NP problem was introduced independently by Stephen Cook and Leonid Levin. Since that date, all efforts to find a proof for this problem have failed. Another major complexity classes are L and NL. Whether L = NL is another fundamental question that it is as important as it is unresolved. We demonstrate if L is not equal to NL, then P = NP. In addition, we show if L is equal to NL, then P = NP. In this way, we prove the complexity class P is equal to NP. Furthermore, we demonstrate the complexity class NL is equal to NP.
\end{abstract}

@@

The $P$ versus $NP$ problem is a major unsolved problem in computer science \cite{CS00}. This is considered by many to be the most important open problem in the field \cite{CS00}. It is one of the seven Millennium Prize Problems selected by the Clay Mathematics Institute to carry a US\$1,000,000 prize for the first correct solution \cite{CS00}. The precise statement of the $P=NP$ problem was introduced in 1971 by Stephen Cook in a seminal paper \cite{CS00}. In 2012, a poll of 151 researchers showed that 126 (83\%) believed the answer to be no, 12 (9\%) believed the answer is yes, 5 (3\%) believed the question may be independent of the currently accepted axioms and therefore impossible to prove or disprove, 8 (5\%) said either do not know or do not care or don't want the answer to be yes nor the problem to be resolved \cite{GA12}.

The $P = NP$ question is also singular in the number of approaches that researchers have brought to bear upon it over the years \cite{DEO10}. From the initial question in logic, the focus moved to complexity theory where early work used diagonalization and relativization techniques \cite{DEO10}. It was showed that these methods were perhaps inadequate to resolve $P$ versus $NP$ by demonstrating relativized worlds in which $P = NP$ and others in which $P \neq NP$ \cite{BA75}. This shifted the focus to methods using circuit complexity and for a while this approach was deemed the one most likely to resolve the question \cite{DEO10}. Once again, a negative result showed that a class of techniques known as $``$Natural Proofs$"$ that subsumed the above could not separate the classes $NP$ and $P$, provided one-way functions exist \cite{RAZ97}. There has been speculation that resolving the $P = NP$ question might be outside the domain of mathematical techniques \cite{DEO10}. More precisely, the question might be independent of standard axioms of set theory. Some results have showed that some relativized versions of the $P = NP$ question are independent of reasonable formalizations of set theory \cite{HOP76}.

It is fully expected that $P \neq NP$ \cite{Pap03}. Indeed, if $P = NP$ then there are stunning practical consequences \cite{Pap03}. For that reason, $P = NP$ is considered as a very unlikely event \cite{Pap03}. Certainly, $P$ versus $NP$ is one of the greatest open problems in science and a correct solution for this incognita will have a great impact not only in computer science, but for many other fields as well \cite{AS17}. Whether $P = NP$ or not is still a controversial and unsolved problem \cite{AS17}. We show some results that prove this outstanding problem with the unexpected solution of $P = NP$.

@@

Cryptography, for example, relies on certain problems being difficult. A constructive and efficient solution to an $\textit{NP--complete}$ problem such as $3SAT$ will break most existing cryptosystems including: Public-key cryptography \cite{HW97}, symmetric ciphers \cite{MM00} and one-way functions used in cryptographic hashing \cite{DKV07}. These would need to be modified or replaced by information-theoretically secure solutions not inherently based on $\textit{P--NP}$ equivalence.

There are enormous positive consequences that will follow from rendering tractable many currently mathematically intractable problems. For instance, many problems in operations research are $\textit{NP--complete}$, such as some types of integer programming and the traveling salesman problem \cite{GJ79}. Efficient solutions to these problems have enormous implications for logistics \cite{CS00}. Many other important problems, such as some problems in protein structure prediction, are also $\textit{NP--complete}$, so this will spur considerable advances in biology \cite{BL98}.

Since all the $\textit{NP--complete}$ optimization problems become easy, everything will be much more efficient \cite{LF09}. Transportation of all forms will be scheduled optimally to move people and goods around quicker and cheaper \cite{LF09}. Manufacturers can improve their production to increase speed and create less waste \cite{LF09}. Learning becomes easy by using the principle of Occam's razor: We simply find the smallest program consistent with the data \cite{LF09}. Near perfect vision recognition, language comprehension and translation and all other learning tasks become trivial \cite{LF09}. We will also have much better predictions of weather and earthquakes and other natural phenomenon \cite{LF09}.

There would be disruption, including maybe displacing programmers \cite{IMP95}. The practice of programming itself would be more about gathering training data and less about writing code \cite{IMP95}. Google would have the resources to excel in such a world \cite{IMP95}.

But such changes may pale in significance compared to the revolution an efficient method for solving $\textit{NP--complete}$ problems will cause in mathematics itself \cite{CS00}. Research mathematicians spend their careers trying to prove theorems, and some proofs have taken decades or even centuries to find after problems have been stated \cite{AS17}. For instance, Fermat's Last Theorem took over three centuries to prove \cite{AS17}. A method that is guaranteed to find proofs to theorems, should one exist of a $``$reasonable$"$ size, would essentially end this struggle \cite{CS00}.
